The `ordertrans()` function

### 2021-07-26 inst/ordertrans.Rmd
more explanation

@@

But note that `x` is not helpfully structured to answer either of
these questions: you have to go searching through the names or the
ranks respectively---both of which may appear in any order---to find
the competitor or rank you are interested in.  What we want is to
rearrange the elements of `x` so that the names are in alphabetical
order.  That way we can see straighaway where competitor `a` placed
(in this case, third).  This nontrivial task is accomplished by
function `ordertrans()`:

>>>>

```{r}
ordertrans
```

@@

But note that `x` is not helpfully structured to answer either of
these questions: you have to go searching through the names or the
ranks respectively---both of which may appear in any order---to find
the competitor or rank you are interested in.  To find the rank vector
(that is, who came first, second etc), one would use `sort()`:

```{r}
sort(x)
```

But this is suboptimal to find the order vector ["where did a
particular competitor come?"].  For the order vector, we want to
rearrange the elements of `x` so that the names are in alphabetical
order.  That way we can see straighaway where competitor `a` placed
(in this case, third).  This nontrivial task is accomplished by
function `ordertrans()`:
